\documentclass[]{essdee-resume}
\usepackage{fancyhdr}
% \usepackage[document]{ragged2e}
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Sounak}{Dey}{ \urlstyle{same} 
North Dumdum, Kolkata - 700049\\
\href{mailto:the.sounak.dey@gmail.com}{the.sounak.dey@gmail.com} | (+91) 9874062971 | \href{mailto:Sounak.Dey@iiitb.ac.in}{sounak.dey@iiitb.ac.in}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{IIIT Bangalore}
\descript{M.Tech in Computer Science}
\location{Ongoing | Bangalore, India}
\location{CGPA: 3.35 / 4.0}
\sectionsep

\subsection{GCETTS}
\descript{B.Tech in Information Tech.}
\location{2019 | Kolkata, India}
\location{DGPA: 8.31 / 10} 
\sectionsep

\subsection{Army Public School}
\location{CBSE | Class XII}
\location{2015 | Barrackpore, India}
\location{Percentage: 86.4\%} 
\sectionsep

\subsection{Army Public School}
\location{CBSE | Class X} 
\location{2013 | Barrackpore, India}
\location{CGPA: 9.6 / 10} 
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Graduate}
CS-511  Algorithms \\
CS-513  Software Systems \\
% AI-511 Machine Learning \\
CS-605  Data Modeling \\
CS-816 Software Production Engg. \\
\sectionsep

\subsection{Undergraduate}
Operating Systems \\
Computer Networks \\
Data Structures \& Algorithms \\
Database Systems \\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{PROGRAMMING}
C \textbullet{} C++ \textbullet{} SQL \textbullet{} CSS \textbullet{} HTML \\
\location{Familiar:}
Java \textbullet{} React \textbullet{} Angular \textbullet{} \LaTeX\  \\
Spring Boot \textbullet{} Bootstrap\\ 
\textbf{Environments:}\\
Linux \textbullet{} Visual Studio Code  \\
IntelliJ IDEA \textbullet{} JupyterLab
\sectionsep

\subsection{Artistic}
Plays the Tabla \\
\sectionsep

\subsection{Languages}
English \textbullet{} Hindi \textbullet{} Bengali \\
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
GitHub:// \href{https://github.com/Sounak-Dey}{\bf sounak-dey} \\
LinkedIn://  \href{https://www.linkedin.com/in/sounak-dey}{\bf sounak-dey} \\
Quora://  \href{https://www.quora.com/profile/Sounak-Dey-2}{\bf Sounak-Dey-2}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}

\runsubsection{NP Lab Reports}
\descript{| Angular + Spring Boot + Jupyter Lab}
\location{Jan 2021 - May 2021}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item A collaboration between the \textbf{E-Health Research Center (EHRC)} of \textbf{IIIT-B} and  \textbf{National Institute of Mental Health and Neuro-Sciences (NIMHANS)}. 
\item The project aims at replacing the current Excel-based format to provide a more suitable format of search engine for the \textbf{diagnosis reports} of the \textbf{Pathology Lab} of \textbf{NIMHANS}, which allows the user to do \textbf{context-based searches} on the reports, that will, in turn, return more efficient results, making the work of the medical staff easier.
\item During the search, it also provides necessary \textbf{recommendations} on the basis of corpus for both site and diagnosis. The project also provides automatic parsing for newly uploaded files. 
\end{tightemize}
\sectionsep

\runsubsection{The Gift Library}
\descript{| React + Spring Boot + CI/CD DevOps}
\location{Apr 2021 - May 2021}
\begin{tightemize}
\item Developed a \textbf{web application}, 'The Gift Library' keeping in mind the need for getting  \textbf{fully personalised gifts} for our dear ones, and the fact that, a solution to this exact problem is yet to exist.
\item Through The Gift Library users will be able to get a gift by contacting the right artists whose work they like (after browsing through them all), and personalise it fully to perfectly fit their requirements .
\item Implemented the \textbf{CI/CD DevOps} toolchain using: \\
Source Control Management - \textbf{Git (GitHub)}, 
Continuous Integration - \textbf{Jenkins}, 
Containerization - \textbf{Docker (DockerHub)},
Continuous Deployment - \textbf{RunDeck}.\\
Monitoring - \textbf{ELK stack(Elastic Search, Logstash, Kibana)}.
\end{tightemize}
\sectionsep

\runsubsection{Mercari Price Suggestion}
\descript{| Kaggle Dataset + Classical ML }
\location{Oct 2020 - Nov 2020}
\begin{tightemize}
\item \textbf{Mercari} is Japan’s biggest community-powered shopping app where sellers are enabled to put just about anything, or any bundle of things.
\item The problem was to build an algorithm that automatically \textbf{suggests} the right \textbf{prices} for these products \textbf{from the user-inputted text descriptions} of their \textbf{products}, including details like product category name, brand name, item condition, etc..
\item We  were  able  to  come up  with  an  efficient \textbf{LightGBM} model  with an  \textbf{RMSLE} score of \textbf{0.436}, to predict the price of a given product online, based on the various information and descriptions we have at our disposal about the product.
\end{tightemize}
\sectionsep






% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %     OTHERS
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Achievements} 
\vspace{\topsep}    % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Achieved an \textbf{All India Rank} of \textbf{1046} out of 1,00,000 candidates (99 \%tile) in 
\textbf{GATE} CS 2019.
\item Recipient of the \textbf{Prime Minister Scholarship}, awarded to top 5000 wards of Ex Defense Personnel, from all over India, based on their class XII board results.
\item Reached the Quarter Finals with Team PEROS at the Open to all VALORANT Tournament of INFIN8 conducted by IIIT Bangalore.
\item \textbf{Runner-up} in \textbf{Student Affairs Council}(SAC) \textbf{Elections} 2020 of IIIT Bangalore.
\end{tightemize}

\section{Hobbies}
\vspace{\topsep}    % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Reading Detective stories.
\item PC Gaming.
\item Watching Anime.
\end{tightemize}

\end{minipage} 
\end{document}  \documentclass[]{article}
